On the Synchronization Power of the Openflow Data Plane

### 2015-04-12 inband-sync.tex
small changes to back and adding draft figs

\emph{FlowMod} is the main messages used in Openflow 
to update the switch configuration. 
In a nutshell, \emph{FlowMod} specifies the type of flow table modification,
a match and an action. 
The standard behavior is that the new rule simply replaces an existing one
with exactly the same match, and is installed
in addition to an existing one if the match only
partially overlaps. The latter can result
in inconsistencies, especially if the old and the new rule
have the same priority. \stefan{liron, is this correct?}\liron{a bit not clear, lets talk about this}
\emph{FlowMod} can be used together with a the CHECK\_OVERLAP flag
of \emph{FlowMod}, in order to detect conflicts: if the flow spaces of an old
and the new rule overlap, 
that is, if there is an entry with overlapping match part but different action, 
 and if the two rules have the same priority, then 
\emph{FlowMod} fails.

@@

>>>>

\emph{FlowMod} is the main messages used in Openflow 
to update the switch configuration. 
In a nutshell, \emph{FlowMod} specifies a new flow entry or the modifications to existing flow entries.
The main properties of each flow entry are: 1) A match defined by a ternary patterns (a value and a mask) over packet header fields, 2) Instructions defined by  a list of modifications to packet action set 3) a cookie value used to reference a single or multiple packets.

%,a match and an action. 
The standard behavior is that the new flow entry simply replaces an existing one
with exactly the same match, and is installed
in addition to an existing one if the match only
partially overlaps. The latter can result
in inconsistencies, especially if the old and the new rule
have the same priority. \stefan{liron, is this correct?}\liron{a bit not clear, lets talk about this}

\emph{FlowMod} can be used together with a the CHECK\_OVERLAP flag
of \emph{FlowMod}, in order to detect conflicts: if the flow spaces of an old
and the new rule overlap, 
that is, if there is an entry with overlapping match part but different action, 
 and if the two rules have the same priority, then 
\emph{FlowMod} fails.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1\columnwidth]{no-sync.png}\\
\caption{}\label{fig:no-sync}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1\columnwidth]{sync-with-cas.png}\\
\caption{}\label{fig:cas-sync}
\end{figure}
